\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-05-09 manuscript_v5/03-results.qmd
updated

@tbl-descriptive-stats shows the characteristics of the data from the Fields COVID-19 survey used for analysis with regard to vaccination status. A total of **6,236** observations were used for analysis, from which 24\% (1,547) corresponded to individuals that reported not having received the first dose of the vaccine. Across the socio-demographic characteristics collected by the survey, higher vaccination uptake was reported by individuals in the highest income bracket considered, those between 16 and 34 years of age, individuals that lived in the East Health Region, and individuals that identified as White or Caucasian. During the months covered by the survey, the highest vaccination uptake was observed in January of 2022.

@@

```{r,model-uncorr-fig}
#| message: false
#| warning: false
#| echo: false
#| fig-align: left
#| fig-width: 7
#| fig-height: 7
#| label: fig-model-uncorr
#| fig-cap: "Coefficient estimates and confidence intervals for the uncorrected model. Only statistically significant interaction terms are shown. Full interaction terms can be found in Supplementary Figure A-3."

@@

# call script that creates figure for model

@@

#call figure created in the script above
uncorr_mod

>>>>

@tbl-descriptive-stats shows the characteristics of the data from the Fields COVID-19 survey used for analysis with regard to vaccination status. A total of **6,236** observations were used for analysis, from which 24.8\% (1,547) corresponded to individuals that reported not having received the first dose of the vaccine. Vaccination rates ranged between 71-79\% across household income brackets, age groups, Health Regions, and the months considered in the survey. However, the highest vaccination rates in each category were reported by individuals in the highest income bracket (79\%), those between 16 and 34 years of age (77\%), individuals that lived in the East Health Region (77\%), and  during January of 2022 (78\%). Differences were higher between racial/ethnic groups, where the higher vaccination rate was reported by White/Caucasian individuals (84\%), against vaccination rates between 63-66\% reported in the case of Arab/Middle Eastern, Black, Indigenous, Latin American individuals, and those that reported belonging to "Other" racial groups, which included Southeast Asian, Filipino, West Asian, and minorities not identified elsewhere.

@@

```{r,models}
#| message: false
#| warning: false
#| echo: false
#| fig-align: left
#| fig-width: 12
#| fig-height: 7
#| label: fig-model-uncorr
#| fig-cap: "Coefficient estimates and confidence intervals for the uncorrected model. Only statistically significant interaction terms are shown. Full interaction terms can be found in Supplementary Figure A-3."

@@

# call script that creates figure for uncorrected model

@@

#call script that creates figure for corrected model
source(here("code","corr_model.R"))

fig_mod<-uncorr_mod+corr_mod+plot_layout(guides = "collect")+plot_annotation(tag_levels = "A")

#print(fig_mod, vp=viewport(angle=90,height = 0.5,clip="off"))
fig_mod

### 2023-05-09 manuscript_v5/main.qmd
updated

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
      - ref: espum
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: crm
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---

@@

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(lme4)
library(lubridate)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)
```

>>>>

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
      - ref: espum
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: crm
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header:
      - text: |
          \usepackage{pdflscape}
      - file: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---

@@

library(weights)
library(here)
library(survey)
library(magrittr)
library(tidyverse)
library(naniar)
library(lme4)
library(lubridate)
library(grid)
library(kableExtra)
library(modelsummary)
library(gtsummary)
library(patchwork)
```

### 2023-05-09 manuscript_v5/main.tex
updated

%line numbers
%\usepackage{mathpazo}
\usepackage{lineno}
\linenumbers

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{caption}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1,2; Bouchra Nasri1,2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

Table~\ref{tbl-descriptive-stats} shows the characteristics of the data
from the Fields COVID-19 survey used for analysis with regard to
vaccination status. A total of \textbf{6,236} observations were used for
analysis, from which 24\% (1,547) corresponded to individuals that
reported not having received the first dose of the vaccine. Across the
socio-demographic characteristics collected by the survey, higher
vaccination uptake was reported by individuals in the highest income
bracket considered, those between 16 and 34 years of age, individuals
that lived in the East Health Region, and individuals that identified as
White or Caucasian. During the months covered by the survey, the highest
vaccination uptake was observed in January of 2022.

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{caption}
%line numbers
%\usepackage{mathpazo}
%\usepackage{rotating}
\usepackage{lineno}
\linenumbers

\usepackage{pdflscape}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata},
  pdfauthor={Ariel Mundo Ortiz1,2; Bouchra Nasri1,2,},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

Table~\ref{tbl-descriptive-stats} shows the characteristics of the data
from the Fields COVID-19 survey used for analysis with regard to
vaccination status. A total of \textbf{6,236} observations were used for
analysis, from which 24.8\% (1,547) corresponded to individuals that
reported not having received the first dose of the vaccine. Vaccination
rates ranged between 71-79\% across household income brackets, age
groups, Health Regions, and the months considered in the survey.
However, the highest vaccination rates in each category were reported by
individuals in the highest income bracket (79\%), those between 16 and
34 years of age (77\%), individuals that lived in the East Health Region
(77\%), and during January of 2022 (78\%). Differences were higher
between racial/ethnic groups, where the higher vaccination rate was
reported by White/Caucasian individuals (84\%), against vaccination
rates between 63-66\% reported in the case of Arab/Middle Eastern,
Black, Indigenous, Latin American individuals, and those that reported
belonging to ``Other'' racial groups, which included Southeast Asian,
Filipino, West Asian, and minorities not identified elsewhere.
